New insights into the Weddell Sea ecosystem applying a network approach

### 2022-11-10 Manuscript/Manuscript.Rmd
First paragraphs Discussion

@@

4)
Our results showed that only few species are key in terms of stability in the Weddell Sea food web. This is in concordance with other studies of complex empirical food webs in high-latitude marine ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022]. Such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.

@@

The conclusion goes here.

>>>>

Using the highest-resolved marine polar food web up to date, we show that 1) the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent; that 2) there is a positive relationship between species mean interaction strength and two unweighted properties, trophic level and degree; and that 3) only few species are key in terms of food web stability, presenting particular weighted and unweighted properties. It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships. After analysing more than 2900 predator-prey interactions from several ecosystems, @Pawar2012 concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning. This arises as crucial to better understand how a complex system such as the Weddell Sea might respond to environmental change, which is an ongoing issue in that region of the Antarctic [@Gutt2022 and references herein].

Our results regarding the distribution of the interaction strengths are consistent with prior theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005]. Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak. Historically, after @May1972 installed the debate complexity-stability, these results have been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.

Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree

@@

4)
Our results showed that only few species are key in terms of stability in the Weddell Sea food web. This is in concordance with other studies of complex empirical food webs in high-latitude marine ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022]. In the present work we propose that such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.

@@

Our analyses provide insights into ...

### 2022-11-10 Manuscript/Manuscript.tex
First paragraphs Discussion

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
\item
  Our results showed that only few species are key in terms of stability
  in the Weddell Sea food web. This is in concordance with other studies
  of complex empirical food webs in high-latitude marine ecosystems
  \citep{Kortsch2015, Marina2018, Rodriguez2022}. Such key species are
  characterized by: 1) high mean interaction strength; 2) mid to high
  trophic level; 3) relatively high number of interactions; and 4) mid
  to low trophic similarity.
\end{enumerate}

@@

The conclusion goes here.

>>>>

Using the highest-resolved marine polar food web up to date, we show
that 1) the distribution of the interaction strength at the food web
level is asymmetric, where weak interactions are prevalent; that 2)
there is a positive relationship between species mean interaction
strength and two unweighted properties, trophic level and degree; and
that 3) only few species are key in terms of food web stability,
presenting particular weighted and unweighted properties. It's also
noteworthy, that our study is the first of its type to consider the
dimensionality of the interaction (2 or 3 dimensions) to estimate
predator-prey relationships. After analysing more than 2900
predator-prey interactions from several ecosystems, \citet{Pawar2012}
concluded that interaction dimensionality is a critical factor driving
consumer-resource dynamics, which will lead to better predictions of
food web and ecosystem functioning. This arises as crucial to better
understand how a complex system such as the Weddell Sea might respond to
environmental change, which is an ongoing issue in that region of the
Antarctic \citep[ and references herein]{Gutt2022}.

Our results regarding the distribution of the interaction strengths are
consistent with prior theoretical and empirical studies
\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005}.
Within a system of a given complexity, commonly only a few strong
species interactions are present with most interactions being weak.
Historically, after \citet{May1972} installed the debate
complexity-stability, these results have been interpreted as an
explanation for the persistence of complex food webs in nature
\citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we showed that
this pattern is also prevalent in one of the most complex empirical
marine food webs that was studied so far, with 490 species and 16041
predator-prey interactions.

Strong relationship between interaction strength and trophic level. Less
stronger but evident relationship with degree

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
\item
  Our results showed that only few species are key in terms of stability
  in the Weddell Sea food web. This is in concordance with other studies
  of complex empirical food webs in high-latitude marine ecosystems
  \citep{Kortsch2015, Marina2018, Rodriguez2022}. In the present work we
  propose that such key species are characterized by: 1) high mean
  interaction strength; 2) mid to high trophic level; 3) relatively high
  number of interactions; and 4) mid to low trophic similarity.
\end{enumerate}

@@

Our analyses provide insights into \ldots{}
